Appendix

### 2020-05-21 appendix/appendixV5.Rmd
commit 2 05/20

```{r, echo=FALSE, include=FALSE}

# Paper 367
dat <- data.frame(
  id = 367,
  published = 'Yes',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'Spatially Targeted Government Spending and
Heterogeneous Constituent Cost Shares',
  author = 'Bradbury and Stephenson',
  year = 2009,
  authoryear = 'Bradbury and Stephenson (2009)',
  journal = 'The Journal of Private Enterprise',
  web = 'http://journal.apee.org/index.php?title=Spring2009_6',
  table = 2,
  column = 2,
  indepvar = 'MEMSENATE',
  indepvar2 = 'K',
  depvar = 'Total Spending per capita',
  depvar2 = 'ExpPC',
  coef = 0.624,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.624/3.10
)

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01262,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.01262/2.12
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.004964,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004964/2.9
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.01134,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.01134/4.52
))

# Paper 585 K
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Upper size',
  indepvar2 = 'K',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = -0.00559,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.00559/2.39
))

# Paper 585 N
dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 5,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003627,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003627/2.51
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 2,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.000517,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.000517/0.47
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 3,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.016946,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.016946/8.65
))

dat <- rbind(dat,
  data.frame(
  id = 585,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Legislative organization and government spending: cross-country evidence',
  author = 'Bradbury and Crain',
  year = 2001,
  authoryear = 'Bradbury and Crain (2001)',
  journal = 'Journal of Public Economics',
  web = 'https://doi.org/10.1016/S0047-2727(00)00150-X',
  table = 2,
  column = 4,
  indepvar = 'Lower size',
  indepvar2 = 'N',
  depvar = 'Percent of GDP',
  depvar2 = 'PCTGDP',
  coef = 0.012337,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.012337/6.65
))

# Paper 505
dat <- rbind(dat,
  data.frame(
  id = 505,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'States',
  location = 'US',
  title = 'The Endogeneity of the Initiative: A Comment on Marschall and Ruhil',
  author = 'Matsusaka',
  year = 2005,
  authoryear = 'Matsusaka (2005)',
  journal = 'State Politics & Policy Quarterly',
  web = 'https://www.jstor.org/stable/40421558',
  table = 1,
  column = 3,
  indepvar = 'Seats',
  indepvar2 = 'N',
  depvar = 'State Government Expenditure per Capita',
  depvar2 = 'ExpPC',
  coef = -0.96,
  scoef = 'N',
  scoefsig = 'N',
  SE = 0.18
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 1,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.018
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.229,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.037
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.455,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.038
))

# Paper 448
dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'IV',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 4,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.411,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.049
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 1,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.226,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.053
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 2,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.213,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.317
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 3,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.185,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.305
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 4,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.235,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.336
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 5,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.374,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.064
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 6,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.811,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.181
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 7,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.795,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.176
))

dat <- rbind(dat,
  data.frame(
  id = 448,
  published = 'Yes',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Italy',
  title = 'Legislature size and government spending in Italian regions: Forecasting the effects of a reform',
  author = 'Fiorino and Ricciuti',
  year = 2007,
  authoryear = 'Fiorino and Ricciuti (2007)',
  journal = 'Public Choice',
  web = '10.1007/s11127-006-9108-y',
  table = 3,
  column = 8,
  indepvar = 'LEG',
  indepvar2 = 'N',
  depvar = 'Per Capita Regional expenditure',
  depvar2 = 'ExpPC',
  coef = 0.849,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.238
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 1,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0109,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0143
))

dat <- rbind(dat,
  data.frame(
  id = 974,
  published = 'No',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'Latin America',
  title = 'Institutional arrangements and fiscal performance: the latin american experience',
  author = 'Stein, Talvi, and Grisanti',
  year = 1998,
  authoryear = 'Stein et al. (1998)',
  journal = 'NBER Working papers',
  web = 'https://www.nber.org/papers/w6358.pdf',
  table = 3,
  column = 4,
  indepvar = 'District magnitude',
  indepvar2 = 'logN',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.0135,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.0121
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.003,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.009,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.011,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 7,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.005,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.003
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 1,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.04,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 2,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.03,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 3,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.01,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.002
))

dat <- rbind(dat,
  data.frame(
  id = 542,
  published = 'Yes',
  usemeta = 0, 
  method = 'PANEL',
  elecsys = 'Mixed',
  elecsys2 = 'Non-Maj',
  agglevel = 'Countries',
  location = 'World',
  title = 'Political Parties and the Size of Government in Multiparty Legislatures: Examining Cross-Country and Panel Data Evidence',
  author = 'Mukherjee',
  year = 2003,
  authoryear = 'Mukherjee (2003)',
  journal = 'Comparative Political Studies',
  web = 'https://journals.sagepub.com/doi/pdf/10.1177/0010414003254240',
  table = 6,
  column = 4,
  indepvar = 'Seats in Lower Chamber',
  indepvar2 = 'N',
  depvar = 'Proportion expenditure GDP',
  depvar2 = 'PCTGDP',
  coef = 0.02,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.004
))

dat <- rbind(dat,
  data.frame(
  id = 886,
  published = 'No',
  usemeta = 1, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Brazil',
  title = 'Electoral systems, legislative fragmentation and public spending: a comparative analysis of brazilian states',
  author = 'Lledo',
  year = 2003,
  authoryear = 'Lledo (2003)',
  journal = NA,
  web = 'http://lasa.international.pitt.edu/Lasa2003/LledoVictor.pdf',
  table = 6,
  column = 1,
  indepvar = 'Log (State Legislature Seats)',
  indepvar2 = 'logN',
  depvar = 'Primary Spending as a share of GSP',
  depvar2 = 'PCTGDP',
  coef = -4.69,
  scoef = 'N',
  scoefsig = NA,
  SE = -4.69/(-1.75)
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 1, 
  method = 'PANEL',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 4,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = 0.001,
  scoef = 'P',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 862,
  published = 'Yes',
  usemeta = 0, 
  method = 'OLS',
  elecsys = 'PR',
  elecsys2 = 'Non-Maj',
  agglevel = 'States',
  location = 'Switzerland',
  title = 'Do large cabinets favor large governments? Evidence on the fiscal commons problem for Swiss Cantons',
  author = 'Schaltegger and Feld',
  year = 2009,
  authoryear = 'Schaltegger and Feld (2009)',
  journal = 'Journal of Public Economics',
  web = 'https://reader.elsevier.com/reader/sd/pii/S0047272708001138?token=ADB01EB80E554D7E01D74DA0D9E36914B6F3D22121C18EC53B328A4863CE63C5457FC87C6A223E12338FD17437D454BF',
  table = 6,
  column = 3,
  indepvar = 'Seats in Parliament',
  indepvar2 = 'N',
  depvar = 'Expenditure per capita',
  depvar2 = 'ExpPC',
  coef = -0.001,
  scoef = 'N',
  scoefsig = NA,
  SE = 0.001
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 3,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.302,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.885
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 1,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.276,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.276/7.185
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 0,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 2,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Log (Expenduture per capita)',
  depvar2 = 'logExpPC',
  coef = 0.295,
  scoef = 'P',
  scoefsig = 'P',
  SE = 0.302/7.545
))

dat <- rbind(dat,
  data.frame(
  id = 849,
  published = 'No',
  usemeta = 1,
  method = 'OLS',
  elecsys = 'Maj',
  elecsys2 = 'Maj',
  agglevel = 'Local',
  location = 'US',
  title = 'Districts, spillovers, and government overspending',
  author = 'Baqir',
  year = 1999,
  authoryear = 'Baqir (1999)',
  journal = NA,
  web = 'http://documents.worldbank.org/curated/en/969221468781782275/pdf/multi-page.pdf',
  table = 3,
  column = 6,
  indepvar = 'Log (Council Size)',
  indepvar2 = 'logN',
  depvar = 'Expenditure Share',
  depvar2 = 'PCTGDP',
  coef = 2.066,
  scoef = 'P',
  scoefsig = 'P',
  SE = 2.066/7.014
))

>>>>

# Build plot function for forest plots
build_forest <- function(mod, capt, lsize = 22) {
  # Build dataset for plot
  mod2 <- tibble(
    TE = mod$TE,
    seTE = mod$seTE,
    studlab = mod$studlab,
    lower = mod$lower,
    upper = mod$upper,
    group = "A") %>%
    bind_rows(.,
              aux = tibble(
                TE = c(mod$TE.random, NA),
                seTE = c(mod$seTE.random, NA),
                studlab = c("Overall Effect", "Prediction Interval"),
                lower = c(mod$lower.random, mod$lower.predict),
                upper = c(mod$upper.random, mod$upper.predict),
                group = "B")) %>%
    group_by(studlab) %>%
    mutate(studlab2 = paste0(studlab, "_", 1:n())) %>%
    ungroup()

  # Build plot
  p <- mod2 %>%
    ggplot(aes(y = reorder(studlab2,TE), x = TE, xmin = lower, xmax = upper)) +
    geom_point(aes(color = group)) +
    geom_errorbarh(aes(color = group), height = 0.1) +
    scale_color_manual(values = c("#000000", "#8b0000")) +
    scale_x_continuous(limits=c(1.2*(min(mod2$lower)), 1.2*(max(mod2$upper)))) +
    scale_y_discrete(labels = function(x) str_replace(x, "_[0-9]*$", "")) + 
    geom_vline(xintercept=0, color="#000000", linetype="dashed") +
    labs(x = "",
         y = "") + 
    facet_grid(group~., scales = "free", space = "free") + 
    labs(caption = capt) +
    theme_minimal() %+replace%
    theme(strip.text.y = element_blank(),
          legend.position = "none",
          axis.text.y = element_text(size = .8*lsize, hjust = 1),
          axis.text.x = element_text(size = .7*lsize, hjust = 1.1),
          plot.caption = element_text(size=lsize))
  return(p)
}
```

```{r, echo=FALSE, include=FALSE}
load('../dataset/dataCoefs.RData')
```
\newpage
## Descriptive statistics
